Commutative character sheaves and geometric types for supercuspidal representations

### 2016-07-18 Geometric types.tex
Updated the bibliography

\bib{Vistoli:notes}{unpublished}{
      author={Vistoli, Angelo},
       title={{Notes on Grothendieck topologies, fibered categories and descent
  theory}},
        date={2007},
        note={\href{http://arxiv.org/abs/math/0412512}{arXiv:0412512
  [math.AG]}},
}

@@

\bib{Yu:models}{inproceedings}{
author={Yu, Jiu-Kang},
title={{Smooth models associated to concave functions in Bruhat-Tits theory}},
%date={2015},
%pages={{579\ndash 622}},
booktitle={{Autour des sch\'emas en groupes - \'Ecole d'\'et\'e franco-asiatique de g\'eom\'etrie alg\'ebrique et de th\'eorie des nombres. Volume III}},
      series={Panoramas et synth\`eses},
      volume={47},
    publisher={Soci\'et\'e Math\'ematique de France},
     issn={1272-3835},
     note={\href{http://smf4.emath.fr/Publications/PanoramasSyntheses/2016/47/html/smf_pano-synth_47_227-258.php}{Panoramas et synth\`eses \textbf{47} (2016), 579--622}}

>>>>

\bib{Vistoli:notes}{article}{
   author={Vistoli, Angelo},
   title={Grothendieck topologies, fibered categories and descent theory},
   conference={
      title={Fundamental algebraic geometry},
   },
   book={
      series={Math. Surveys Monogr.},
      volume={123},
      publisher={Amer. Math. Soc., Providence, RI},
   },
   date={2005},
   pages={1--104},
%   review={\MR{2223406}},
}

@@

\bib{Yu:models}{inproceedings}{
author={Yu, Jiu-Kang},
title={{Smooth models associated to concave functions in Bruhat-Tits theory}},
%date={2015},
%pages={{579\ndash 622}},
booktitle={{Autour des sch\'emas en groupes - \'Ecole d'\'et\'e franco-asiatique de g\'eom\'etrie alg\'ebrique et de th\'eorie des nombres. Volume III}},
      series={Panoramas et synth\`eses},
      volume={47},
    publisher={Soci\'et\'e Math\'ematique de France},
     issn={1272-3835},
     note={\href{http://smf4.emath.fr/Publications/PanoramasSyntheses/2016/47/html/smf_pano-synth_47_227-258.php}{Panoramas et synth\`eses \textbf{47} (2015), 227--258}}
